\chapter{Conclusion}
\label{chap:conclusion}

\section{State-of-the-art} Having a prefetch policy in place cuts a third of the execution time and increases energy consumption by just 9.05\% units. A comparison of an early prefetch
(OnExecute) with a late one (OnCommit) shows that the later one increases runtime
by a little over 1\% units, but energy increases by 33.13\% units.

\section{Techniques to reduce speculation effect}  OnNonBSpec with Re-Execute is the fastest store prefetch policy (96.58\%) with a speedup of 3.42\%
units compared to OnCommit, but it burns 9.42\% units more energy. Given these results OnNonBSpec with ReExecute was the best up to this point. 

\section{Techniques to filter unnecessary speculations} The SameCasheLine filter proved to have no impact on runtime but saved energy and was therefore used together with Re-Execute on all new (from this point) policies. OnNonBSpec is still the fastest policy, but PCBased4 is more energy efficient with 0.30\% more time for 6.17\% less energy.

\section{Techniques for timeLiness} 
After considering the final techniques introduced by this thesis, OnNonBSpec with
Re-Execute and SameCacheLine is still the fastest one with 96.58\% at an energy
cost of 109.42\%. When it comes to energy consumption, PCBasedTL3 8 with Re-Execute
and SameCacheLine takes the lead with 98.16\%. That is lower then OnCommit
(100.00\%); the only policy that burns less is NoPrefetch (90.95\%). In terms of runtime
PCBasedTL3 8 with Re-Execute and SameCacheLine gets 97.51\% which is 0.93\%
units slower then OnNonBSpec with Re-Execute and SameCacheLine. On the other
hand, it instead burns 11.28\% units more energy. These numbers on energy and runtime lead to the conclusion that PCBasedTL3 8 with Re-Execute and SameCacheLine must be the prefetch
policy to use.
